---
title: "Hello R"
author: "John Nobles"
date: "Data 2401"
output: 
  html_document: 
    fig_width: 6
    fig_height: 6
    highlight: textmate
    theme: simplex
---

MAKE SURE YOU READ AND FOLLOW **ALL** INSTRUCTIONS ON THE INSTRUCTION DOCUMENT.

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```

### Exercise 1

-   datasaurus_dozen has 1846 rows and 3 columns.

-   It has the variables "x", "y", and "dataset".

### Exercise 2

-   Let's plot the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

-   Let's calculate the correlation coefficient of the dino dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

-   Let's plot the star dataset:

```{r plot-star}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

-   Let's use R to calculate the correlation coefficient of the star dataset:

```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))
```

### Exercise 4

-   Let's plot the circle dataset:

```{r plot-circle}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")
ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

-   Let's calculate the correlation coefficient for the circle dataset:

```{r cor-circle}
circle_data %>%
  summarize(r = cor(x, y))
```

### Exercise 5

-   Let's plot all the datasets:

```{r plot-all}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+
  geom_point()+
  facet_wrap(~ dataset, ncol = 3) +
  theme(legend.position = "none")
```

-   Let's find the correlation coefficient of all the datasets:

```{r cor-all}
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y)) 
```
